% !TeX root = ../main.tex

\chapter{研究資料與方法}

\section{研究資料}
Our research is based on past studies in the Ilan Plain, specifically the National Energy Program Phase I (NEP1) and National Energy Program Phase II (NEP2). NEP1, which deployed from 2009 to 2013, focused on formulating energy policies, promoting energy technology research and development, and advancing carbon reduction and energy conservation measures. NEP2, lasting from 2014 to 2018, aimed to further develop Taiwan's energy technology, particularly in geothermal energy, natural gas hydrates, and renewable energy.

\section{前處理}
In data processing, we begin with preprocessing steps to ensure accurate analysis. The first step is instrument calibration, which involves removing the instrument response to correct for any distortions introduced by the equipment. Following this, we downsample the data to a lower rate of 20 Hz to reduce the data size and computational load while retaining essential information. We then apply a bandpass filter (? - ? Hz) to remove noise and isolate the frequency range of interest. Additional preprocessing includes tapering, which minimizes edge effects by gradually reducing signal amplitude at the beginning and end of the recording; detrending, which removes any linear trends from the data to focus on variations; and demeaning, which subtracts the mean value from the data to center the signal around zero. These steps collectively enhance the quality of the data and prepare it for subsequent analysis. Removing linear trend and demean should before applying bandpass filter, so, this paragraph could be simplied as follows,

\section{分析}

For the data analysis, we applied the method called H/V spectral ratio, which was calculated by averaging the H/V ratios obtained by dividing the signal into non-overlapping 30-second windows within each 5-hour recording period. Each window was then Fast Fourier Transformed (FFT) to analyze the frequency components and smoothed using triangular functions with a width equal to 10% of the central frequency.\par

\section{H/V Microtremor Measurements}
青青子衿，悠悠我心。但為君故，沉吟至今。

\section{DOP-E}
去日苦多。

\subsection{degree-of-polarization}
對酒當歌，人生幾何！譬如朝露，去日苦多。
\subsection{Rayleigh waves ellipticity}
，去日苦多。
\subsection{Rayleigh waves back azimuth}
，去日苦多。
\subsection{Neighbourhood algorithm}
，去日苦多。